---
title: "LMwithPred"
author: "Bethanee Olmos"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the linear model with prediction problem. Predict strength scores using date from the following website

$H_A$ There is a difference in the models, one is better than the other.

$H_0$ There is no difference in the models, one is not better than the other. 

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot)
```

### Model 1

```{r}
plot(SIMS~ARM,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```



```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
New=data.frame(GRIP=94, ARM=88)
predict.lm(model.1,New,interval="prediction")
```

## Model 2

```{r}
plot(SIMS~GRIP,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
predict.lm(model.2,New,interval="prediction")
``` 

## Model 3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=dataF)
summary.lm(model.3)
predict.lm(model.3,New,interval="prediction")
``` 

## Compare

```{r}
anova(model.1,model.3)
```

## Conclusion

As seen above, the P value is less than 1 which means we reject the null hypothesis. We conclude that there is a difference between the models and one of them is bigger than the other two. We concluded that based on the adjusted R-squared which was higher for model 1 than the other two models. 
